---
title: "Exam_Github"
output: html_document
date: "2023-06-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The usethis package makes working with git and GitHub from R and RStudio much easier.

```{r}
install.packages("usethis")
```
2.4 Set-up

Now you have to configure your name and email associated with your GitHub account. Go to RStudio and, using your own identification, type:

```{r}
library(usethis)
use_git_config(
  user.name = "emiliehv", 
  user.email = "emilie.hernes.vereide@hi.no"
  )
```

2.5 Connect RStudio and GitHub

GitHub needs to validate who you are before you can connect it and RStudio. We can do this by generating and saving a Personal Access Token (PAT). You need to do this once for every RStudio project.

```{r}
usethis::create_github_token()
```

This function will open GitHub. After confirming your password, you will be shown a page to make a new PAT. You don’t need to change any of the options. Just click the green “Generate token” button at the bottom of the page.

The next page will show you your PAT. Copy it by clicking on the clipboard icon and return to R.

Now run

```{r}
gitcreds::gitcreds_set()
```

```{r}
git_vaccinate()
```

2.6 Making a repo

Now you are ready to start using RStudio and GitHub. There are two main workflows:

Make a new local repo and push it to GitHub
Clone an existing repo from GitHub onto your computer
We will cover these in turn: choose the best one for your circumstances.

By default, repositories on GitHub are publicly readable. They can be made private if necessary.

```{r}
usethis::use_git()
```











